\documentclass[12pt]{exam}
\usepackage[margin=0.1in]{geometry}

\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{xcolor}
\usepackage{tikz}
\usetikzlibrary{arrows.meta,positioning,shapes.callouts}

\newcommand{\tfq}[3]{%
  \question[#1]\textbf{T/F:} #2%
  % Only show the choices when printing answers/keys
  \ifprintanswers
    \par\begin{oneparchoices}
      #3
    \end{oneparchoices}
  \fi
}



\makeatletter
\newcommand{\TFQ@choices}{} % temp holder

\newenvironment{tfqverb}[2]{%
  \def\TFQ@choices{#2}% store choices for use at end
  \question[#1]\textbf{T/F:}%
}{%
  \ifprintanswers
    \par\begin{oneparchoices}\TFQ@choices\end{oneparchoices}
  \fi
}
\makeatother

%\printanswers
% optional styling for the correct choice:
\CorrectChoiceEmphasis{\bfseries}    % make the correct choice bold
% or e.g. \CorrectChoiceEmphasis{\color{red}\bfseries}

\usepackage{fancyvrb}
\newsavebox{\verbbox}

\begin{document}


\begin{center}
\textbf{\Large Review 3 — Database Management Systems}

\textbf{CSC 3300 \quad Spring 2026}
\end{center}

\begin{questions}
%---------------------------------TRUE/FALSE---------------------------------
\section*{Part I — True/False}

\begin{minipage}{\linewidth}
\question[3]
True or False: Consider the following scenario involving a view definition and an insertion operation. 
The count of rows returned by the last command remains unchanged before and after the insertion. Is it true or false?\par\vspace{0.5em}
\begin{verbatim}
create view history_instructors as
select * 
from instructor
where dept_name= 'History';

insert into history_instructors values ('25566', 'Brown', 'Biology', 100000);

select count(*) from history_instructors;
\end{verbatim}
\begin{checkboxes}
    \CorrectChoice True
    \choice False
\end{checkboxes}
\end{minipage}\vspace{1em}

\begin{minipage}{\linewidth}
\question[2]
True or False: Consider relation R with attributes A, B, C, D. Constraint \textit{unique} (A, B) on this relation 
ensures that no two of its tuples have the same values for attributes A and B.\par\vspace{0.5em}
\begin{checkboxes}
    \CorrectChoice True
    \choice False
\end{checkboxes}
\end{minipage}\vspace{1em}

\begin{minipage}{\linewidth}
\question[2]
True or False: Deletion of a tuple from the \textbf{department} relation may result in the deletion of some tuples from other relations.\par\vspace{0.5em}
\begin{checkboxes}
    \choice True
    \CorrectChoice False
\end{checkboxes}
\end{minipage}\vspace{1em}

\begin{minipage}{\linewidth}
\question[2]
True or False: Definition of the \textit{prereq} table could be changed from: \par\vspace{0.5em}
\begin{verbatim}
create table prereq
(course_id        varchar(8), 
prereq_id        varchar(8),
primary key (course_id, prereq_id),
foreign key (course_id) references course(course_id) on delete cascade,
foreign key (prereq_id) references course(course_id)
);
\end{verbatim}
to\par\vspace{0.5em}
\begin{verbatim}
create table prereq
(course_id        varchar(8), 
prereq_id        varchar(8),
primary key (course_id, prereq_id),
foreign key (course_id) references course(course_id) on delete cascade,
foreign key (prereq_id) references course(course_id) on delete cascade
);
\end{verbatim}
\begin{checkboxes}
    \CorrectChoice True
    \choice False
\end{checkboxes}
\end{minipage}\vspace{1em}

\begin{minipage}{\linewidth}
\question[2]
True or False: It is possible to delete successfully any tuple from any relation of any University Database instance.\par\vspace{0.5em}
\begin{checkboxes}
    \choice True
    \CorrectChoice False
\end{checkboxes}
\end{minipage}\vspace{1em}

\begin{minipage}{\linewidth}
\question[2]
True or False: If we try to delete a tuple from the \textbf{advisor} relation, the tuple is not deleted. 
Instead, \textbf{i\_id} of this tuple is set to NULL.\par\vspace{0.5em}
\begin{checkboxes}
    \choice True
    \CorrectChoice False
\end{checkboxes}
\end{minipage}\vspace{1em}

\begin{minipage}{\linewidth}
\question[2]
True or False: JDBC drivers implement the JDBC API.\par\vspace{0.5em}
\begin{checkboxes}
    \CorrectChoice True
    \choice False
\end{checkboxes}
\end{minipage}\vspace{1em}

\begin{minipage}{\linewidth}
\question[2]
True or False: A function has only input parameters and can return multiple values.\par\vspace{0.5em}
\begin{checkboxes}
    \choice True
    \CorrectChoice False
\end{checkboxes}
\end{minipage}\vspace{1em}

\begin{minipage}{\linewidth}
\question[2]
True or False: If f was a stored function with one parameter of type varchar(20) returning an integer, then the following command would work.\par\vspace{0.5em}
select f('HelloThere') = 1;\par\vspace{0.5em}
\begin{checkboxes}
    \CorrectChoice True
    \choice False
\end{checkboxes}
\end{minipage}\vspace{1em}

\begin{minipage}{\linewidth}
\question[4]
True or False: The execution of this Java code snippet inserts exactly one record into the instructor table.\par\vspace{0.5em}
\begin{verbatim}
	String id = "225";
	String name = "Green";
	String dept_name = "Comp. Sci.";
	BigDecimal salary = new BigDecimal(98000);
	PreparedStatement pstmt = conn.prepareStatement(
        "insert into instructor values (?, ?, ?, ?)");
	pstmt.setString(1, id);
	pstmt.setString(2, name);
	pstmt.setString(3, dept_name);
	pstmt.setBigDecimal(4, salary);
	pstmt.executeUpdate();
	id = "226";
	name = "Brown";
	pstmt.setString(1, id);
	pstmt.setString(2, name);
	pstmt.executeUpdate();
\end{verbatim}
Assume the code runs successfully: there are no instructors with the given IDs and there is a 'Comp. Sci.' department.\par\vspace{0.5em}
\begin{checkboxes}
    \choice True
    \CorrectChoice False
\end{checkboxes}
\end{minipage}\vspace{1em}

\begin{minipage}{\linewidth}
\question[2]
True or False: Dynamic SQL allows the program to construct an SQL query as a character string at runtime, submit the query, 
and then retrieve the result into program variables a tuple at a time.\par\vspace{0.5em}
\begin{checkboxes}
    \CorrectChoice True
    \choice False
\end{checkboxes}
\end{minipage}\vspace{1em}

\begin{minipage}{\linewidth}
\question[2]
True or False: A trigger can only execute after a specified operation (INSERT, UPDATE, DELETE) has completed.\par\vspace{0.5em}
\begin{checkboxes}
    \choice True
    \CorrectChoice False
\end{checkboxes}
\end{minipage}\vspace{1em}

\begin{minipage}{\linewidth}
\question[2]
True or False: In a database management system, the execution of a trigger can cause another trigger to execute.\par\vspace{0.5em}
\begin{checkboxes}
    \CorrectChoice True
    \choice False
\end{checkboxes}
\end{minipage}\vspace{1em}
%---------------------------------MC---------------------------------
\section*{Part II — Multiple choice (choose one)}
\begin{minipage}{\linewidth}
\question[3]
What is the effect of adding the following constraint:\par
\begin{verbatim}
unique (s_ID, i_ID)
\end{verbatim}
to the definition of the \textbf{advisor} relation?\par\vspace{0.5em}
\begin{checkboxes}
    \CorrectChoice The constraint does not impose any additional restrictions.
    \choice Every student is able to have at most one advisor and every instructor is able to have at most one advisee.
    \choice \textbf{i\_ID} attribute can't have value null.
    \choice \textbf{s\_ID} and \textbf{i\_ID} can not both be null.
\end{checkboxes}
\end{minipage}\vspace{1em}

%---------------------------------MS---------------------------------
\section*{Part III — Multiple select (select all that apply)}

\begin{minipage}{\linewidth}
\question[4]
Which of the given statements are true of a view?\par\vspace{0.5em}
\begin{checkboxes}
    \CorrectChoice Some reasons for creating views are security and convenience.
    \CorrectChoice Whenever we evaluate a query in which a view relation occurs, that view relation is replaced 
    with the saved query expression that defines that view.
    \choice A view is not reusable.
    \choice Whenever we define a view, the database system stores the result of evaluation of the query 
    expression that defines the view, rather than the definition of the view.
\end{checkboxes}
\end{minipage}\vspace{1em}

\begin{minipage}{\linewidth}
\question[6]
Consider the following view, named myView, defined in the University database.\par\vspace{0.5em}
\begin{verbatim}
create view myView as
select name, dept_name
from instructor;
\end{verbatim}
Which of the given SQL statements are allowed on the view?\par\vspace{0.5em}
\begin{checkboxes}
    \CorrectChoice select name, dept\_name from myView
    \CorrectChoice select * from department natural join myView
    \CorrectChoice create view nextView as select dept\_name, count(*) from myView group by dept\_name
    \choice insert into myView values ('Grey', 'Comp. Sci.')
\end{checkboxes}
\end{minipage}\vspace{1em}


\begin{minipage}{\linewidth}
\question[6]
Which values can TODO be replaced with so that the query below runs?\par\vspace{0.5em}
\begin{verbatim}
insert into instructor values ('6667', TODO, 'Comp. Sci.', null)
\end{verbatim}
\par\vspace{0.5em}
\begin{checkboxes}
    \CorrectChoice \begin{verbatim} (select version()) \end{verbatim}
    \CorrectChoice 
    \begin{verbatim} 'Green', null, null); -- \end{verbatim}
    \vspace{-0.5em}
    {\footnotesize Note: assume there is a space after the two minus signs (\texttt{-- }).}
    \CorrectChoice \begin{verbatim} (select count(*) from information_schema.schemata) \end{verbatim}
    \choice \begin{verbatim}'\end{verbatim}
    \vspace{-0.5em}
    {\footnotesize Note: the above is a single quote.}
\end{checkboxes}
\end{minipage}\vspace{1em}

\begin{minipage}{\linewidth}
\question[4]
Which statements are true regarding the following function and the query that follows?\par\vspace{0.5em}

\begin{verbatim}
create function instructors_no_fun
(dept_name varchar(20))
returns integer
begin
declare d_count integer;
select count(*) into d_count 
from instructor where instructor.dept_name = dept_name;
return d_count;
end
\end{verbatim}

{\footnotesize Note: To create a function in MySQL Workbench, wrap the function definition with

\texttt{delimiter //} 

before it, and 

\texttt{// delimiter ;}

after it.}

\par\vspace{0.5em}

{\footnotesize Hint: If you get an error when creating the function, try running}
\begin{verbatim}
SET GLOBAL log_bin_trust_function_creators = 1;
\end{verbatim}
{\footnotesize This allows function creation when binary logging is enabled.}

\par\vspace{0.5em}

Consider the following query:

\begin{verbatim}
select dept_name, instructors_no_fun(dept_name)
from department;
\end{verbatim}

\par\vspace{0.5em}

\begin{checkboxes}
    \CorrectChoice dept\_name, of type varchar(20), is the only parameter of the function instructors\_no\_fun.
    \CorrectChoice The query returns, for each department, the number of instructors associated with it.
    \choice For departments with instructors, the query returns the instructor count.
    \CorrectChoice The query runs function instructors\_no\_fun as many times as there are tuples in the table department.
\end{checkboxes}
\end{minipage}\vspace{1em}

\begin{samepage}
\question[6]
Which statements, if any, are true about the below trigger?\par\vspace{0.5em}
\begin{verbatim}
create trigger credits_earned 
after update on takes
for each row
begin
    if (new.grade <> 'F' and new.grade is not null and 
        (old.grade = 'F' or old.grade is null)) 
    then
        update student
        set tot_cred = tot_cred + (select credits
                                   from course
                                   where course.course_id = new.course_id)
        where student.id = new.id;
    end if;
end
\end{verbatim}

\begin{checkboxes}
\CorrectChoice The following query will result in as many updates of some \textit{tot\_cred} values of \textbf{student} 
as there are nulls for the \textit{grade} attribute of \textbf{takes}.
\begin{verbatim}
update takes set grade = 'D' where grade is null
\end{verbatim}

\choice The trigger body will be executed at least once when the query \textit{delete from takes where grade is null} 
is executed, provided some students have ungraded course sections.

\choice Assume that there are only the following tuples in the database.

\textbf{student}

\begin{tabular}{|l|l|l|l|}
\hline
id & name & dept\_name & tot\_cred \\
\hline
'5' & 'Brown' & null & 0 \\
\hline
\end{tabular}

\textbf{course}

\begin{tabular}{|l|l|l|l|}
\hline
course\_id & title & dept\_name & credits \\
\hline
'3300' & 'DBMS' & null & 3 \\
\hline
\end{tabular}

\textbf{section}

\begin{tabular}{|l|l|l|l|l|l|l|}
\hline
course\_id & sec\_id & semester & year & building & room\_number & time\_slot\_id \\
\hline
'3300' & '1' & 'Fall' & 2024 & null & null & null \\
\hline
\end{tabular}

\textbf{takes}

\begin{tabular}{|l|l|l|l|l|l|}
\hline
id & course\_id & sec\_id & semester & year & grade \\
\hline
'5' & '3300' & '1' & 'Fall' & 2024 & null \\
\hline
\end{tabular}

The following update command will execute the body of the \textit{credits\_earned} trigger.
\begin{verbatim}
update student set tot_cred = tot_cred + 
(select sum(credits) from course natural 
join takes where takes.id = student.id and 
student.id = '5' and grade is null)
\end{verbatim}
\choice Assume that there are only the following tuples in the database.

\textbf{student}

\begin{tabular}{|l|l|l|l|}
\hline
id & name & dept\_name & tot\_cred \\
\hline
'5' & 'Brown' & null & 0 \\
\hline
\end{tabular}

\textbf{course}

\begin{tabular}{|l|l|l|l|}
\hline
course\_id & title & dept\_name & credits \\
\hline
'3300' & 'DBMS' & null & 3 \\
\hline
\end{tabular}

\textbf{section}

\begin{tabular}{|l|l|l|l|l|l|l|}
\hline
course\_id & sec\_id & semester & year & building & room\_number & time\_slot\_id \\
\hline
'3300' & '1' & 'Fall' & 2024 & null & null & null \\
\hline
\end{tabular}

\textbf{takes}

\begin{tabular}{|l|l|l|l|l|l|}
\hline
id & course\_id & sec\_id & semester & year & grade \\
\hline
'5' & '3300' & '1' & 'Fall' & 2024 & '' \\
\hline
\end{tabular}

The following update command will execute the body of the \textit{credits\_earned} trigger.
\begin{verbatim}
update takes set grade = 'D' where id = '5' and grade is null
\end{verbatim}
\end{checkboxes}
\end{samepage}

\begin{samepage}
\question[4]
Considering the commands shown below were executed on a University database server with users Grey, Amit, Green, and Brown,
which users have the authority to move all Computer Science Department students who enrolled in CS-190 during the Spring 2009 
semester to section 2 of the course (assume section 2 has already been created)?\par\vspace{0.5em}
In other words, which users can successfully execute the following query?\par\vspace{0.5em}
\begin{verbatim}
update takes
set sec_id = 2
where id in (select id from student where dept_name = 'Comp. Sci.')
and course_id = 'CS-190'
and semester ='Spring'
and year = 2009
\end{verbatim}
Executed Commands:\par\vspace{0.5em}
\begin{verbatim}
create role 'teaching_assistant'@'localhost';
create role 'lecturer'@'localhost';
create role 'dean'@'localhost';

grant select on university.takes to 'teaching_assistant'@'localhost';
grant update on university.takes to 'teaching_assistant'@'localhost';

grant select on university.student to 'lecturer'@'localhost';

grant select on university.instructor to 'dean'@'localhost';

grant 'teaching_assistant'@'localhost' to 'lecturer'@'localhost';
grant 'lecturer'@'localhost' to 'dean'@'localhost';

grant 'dean'@'localhost' to 'Grey'@'localhost';
grant 'dean'@'localhost' to 'Amit'@'localhost';
grant update on university.instructor to 'Amit'@'localhost';

grant 'lecturer'@'localhost' to 'Brown'@'localhost';
grant update on university.student to 'Brown'@'localhost';

grant 'teaching_assistant'@'localhost' to 'Green'@'localhost';
\end{verbatim}

Hint: \\
To test this scenario in MySQL, make sure to enable the default roles for each user by executing:\par\vspace{0.5em}
\begin{verbatim}
SET DEFAULT ROLE ALL TO  'Brown'@'localhost';
SET DEFAULT ROLE ALL TO  'Grey'@'localhost';
SET DEFAULT ROLE ALL TO  'Amit'@'localhost';
SET DEFAULT ROLE ALL TO  'Green'@'localhost';
\end{verbatim}
(More on that in the MYSQL documentation under MySQL :: MySQL 8.0 Reference Manual :: 8.2.10 Using Roles .)

Important: To correctly test this scenario, each user must run the following two commands after logging in, before executing the UPDATE query:\par\vspace{0.5em}
\begin{enumerate}
    \item Activate all granted roles for the current session:
    \begin{verbatim}
SET ROLE ALL;
    \end{verbatim}

    \item Select the appropriate database:
    \begin{verbatim}
USE university;
    \end{verbatim}
\end{enumerate}
\begin{checkboxes}
    \CorrectChoice Amit
    \CorrectChoice Brown
    \choice Green
    \CorrectChoice Grey
\end{checkboxes}
\vspace{1em}
\end{samepage}

\end{questions}
\end{document}