\documentclass[12pt,answers]{exam}

\input{preamble.tex}

\begin{document}
\noindent Name:\ \makebox[3in]{\hrulefill}
\begin{questions}

% ------------------ TRUE/FALSE SECTION ------------------
\section*{Part I — True/False}

\begin{minipage}{\linewidth}
\question[2]
Is it true that the following user requirements translate into the functional dependency shown below?

User requirements:
The database records for each car its VIN number, color, make, model, license\_plate, production\_year.
VIN uniquely identifies the car.

Proposed functional dependency:
VIN \(\to\) color, make, model, license\_plate, production\_year
\begin{checkboxes}
    \CorrectChoice True
    \choice False
\end{checkboxes}
\end{minipage}

\begin{minipage}{\linewidth}
\question[2]
True or False: If $\alpha$, $\beta$, and $\gamma$ are sets of attributes, and the 
functional dependencies $\alpha \to \beta$ and $\beta \to \gamma$ hold, then 
the functional dependency $\alpha \to \gamma$ also holds.

\begin{checkboxes}
    \CorrectChoice True
    \choice False
\end{checkboxes}
\end{minipage}


\begin{minipage}{\linewidth}
\question[2]
True or False: If a schema is decomposed into 3NF using its functional dependencies, the resulting decomposition preserves those dependencies.

\begin{checkboxes}
    \CorrectChoice True
    \choice False
\end{checkboxes}
\end{minipage}


% ------------------ MULTIPLE CHOICE SECTION ------------------
\section*{Part II — Multiple choice (choose one)}

\begin{minipage}{\linewidth}
\question[2]
MongoDB is what type of database?

\begin{checkboxes}
    \choice Key–Value Database
    \CorrectChoice Document Database
    \choice Column-Family Database
    \choice Graph Database
\end{checkboxes}
\end{minipage}





\begin{minipage}{\linewidth}
\question
Which of the following functional dependencies are \emph{trivial}?  
Assume \texttt{ID} is a unique student identifier and \texttt{name} is the student’s name (as in the University Database).

\begin{checkboxes}
    \CorrectChoice ID, name $\to$ ID
    \CorrectChoice name $\to$ name
    \choice ID $\to$ name
    \choice name $\to$ ID
\end{checkboxes}
\end{minipage}




\begin{minipage}{\linewidth}
\question[4]
Consider the relation with attributes $(A, B, C, D, E)$ and the functional dependency $D \to A, C, E$.
Assume that $\{D\}$ and $\{C, E\}$ are superkeys of this relation.

If we want the database to be in Boyce--Codd Normal Form (BCNF), what should be done?

\begin{checkboxes}
    \CorrectChoice Nothing; the relation already satisfies BCNF.
    \choice The relation violates BCNF, and should be decomposed into $(D, A, C, E)$ and $(D, B)$.
    \choice The relation violates BCNF, and should be decomposed into two relations (A, B, C, E) and (D, A, C, E).
    \choice The relation violates BCNF, and should be decomposed into two relations (C, E, D) and (A, B, D).
\end{checkboxes}
\end{minipage}




\end{questions}

\end{document}