\documentclass[12pt,answers]{exam}

\input{preamble.tex}

\begin{document}
\noindent Name:\ \makebox[3in]{\hrulefill}
\begin{questions}

% ------------------ TRUE/FALSE SECTION ------------------
\section*{Part I — True/False}

\begin{minipage}{\linewidth}
\question[2]
True or False: TODO
\begin{checkboxes}
    \CorrectChoice True
    \choice False
\end{checkboxes}
\end{minipage}

% ------------------ MULTIPLE CHOICE SECTION ------------------
\section*{Part II — Multiple choice (choose one)}

\begin{minipage}{\linewidth}
\question[2]
Some documents in the movies collection of the sample\_mflix database have a cast field.
One such document contains the following value for that field.
In this case, cast is an array of strings.
\begin{verbatim}
"cast": [
  "A.C. Abadie",
  "Gilbert M. 'Broncho Billy' Anderson",
  "George Barnes",
  "Justus D. Barnes"
]
\end{verbatim}

\begin{checkboxes}
\CorrectChoice True
\choice False
\choice Prefer not to answer
\end{checkboxes}
\end{minipage}


\begin{minipage}{\linewidth}
\question[2]
The type of a field in a MongoDB document can itself be a document.

\begin{checkboxes}
    \CorrectChoice True
    \choice False
    \choice Prefer not to answer
\end{checkboxes}
\end{minipage}

\begin{minipage}{\linewidth}
\question[2]
What does \textbf{Consistency (C)} mean in the CAP theorem?

\begin{checkboxes}
    \choice The system continues processing reads and writes even when some nodes or groups of nodes cannot communicate with each other.
    \choice During a network partition, the system allows reads and writes to proceed on any nodes that remain reachable.
    \CorrectChoice All reads return the same, most up-to-date value, as if there were a single correct copy of the data.
    \choice Prefer not to answer
\end{checkboxes}
\end{minipage}


\begin{minipage}{\linewidth}
\question[2]
Consider the following aggregation query on the \texttt{sample\_mflix} database:

\begin{verbatim}
db.movies.aggregate([
  {
    $lookup: {
      from: "comments",
      localField: "_id",
      foreignField: "movie_id",
      as: "comments"
    }
  }
]);
\end{verbatim}

To improve performance, which additional index would be most helpful?

\begin{checkboxes}
    \choice An index on \texttt{\_id} in the \texttt{movies} collection.
    \CorrectChoice An index on \texttt{movie\_id} in the \texttt{comments} collection.
    \choice An index on \texttt{\_id} in the \texttt{comments} collection.
    \choice Prefer not to answer
\end{checkboxes}

\end{minipage}


\question[2]
What is the main purpose of sharding in MongoDB?

\begin{checkboxes}
    \CorrectChoice To distribute a large dataset across multiple servers so the system can scale beyond the limits of a single machine.
    \choice To maintain multiple copies of the same data for redundancy.
    \choice To ensure all queries always read from the most up-to-date copy of the data.
    \choice Prefer not to answer
\end{checkboxes}



\end{questions}

\end{document}