\documentclass[12pt, addpoints, answers]{exam}
\input{preamble.tex}

% Header/footer formatting
\pagestyle{headandfoot}
\runningheadrule
\firstpageheadrule
\firstpageheader{Database Management Systems}{Ch 8 Old}{Fall 2025}
\runningheader{}{Ch 8 Old}{}
\runningfooter{}{}{}

\begin{document}
\noindent Name:\ \makebox[3in]{\hrulefill}\hfill Points Scored: \underline{\hspace{3em}} / \numpoints
\begin{questions}

% ------------------ TRUE/FALSE SECTION ------------------
\section*{Part I — True/False}

\begin{minipage}{\linewidth}
\question[2]
True or False: It is not always possible that all the tables of a schema are in BCNF 
(Boyce-Codd Normal Form) and functional dependencies are preserved.\par\vspace{0.5em}
\begin{checkboxes}
    \CorrectChoice True
    \choice False
\end{checkboxes}
\end{minipage}\vspace{1em}


% ------------------ MULTIPLE CHOICE SECTION ------------------

\section*{Part II — Multiple choice (choose one)}

\begin{minipage}{\linewidth}
\question[4]
What is a lossless join decomposition (LJD) of a relation?\textbf{section}?\par\vspace{0.5em}
\begin{checkboxes} 
    \CorrectChoice The decomposition is a LJD if the natural join of the relations in the decomposition produces the original relation.
    \choice The decomposition is a LJD if the natural join of the relations in the decomposition produces the relation with all attributes of the original relation.
    \choice The decomposition is a LJD if there does not exist a functional dependency X->Y, such that X U Y is not a subset of any R.
    \choice The decomposition is a LJD if there exists a functional dependency X->Y holding on a decomposed relation and primary key of one of the new relations is X.
\end{checkboxes}
\end{minipage}\vspace{1em}

% ------------------ MULTIPLE SELECT SECTION ------------------
\section*{Part III — Multiple select (select all that apply)}

\begin{minipage}{\linewidth}
\question[4]
Consider the following relation disk\_drive(serial\_number, manufacturer, model, batch, capacity, retailer). 
Each tuple in the relation disk\_drive contains information about a disk drive with a unique serial\_number, made by a manufacturer,
with a particular model, released in a certain batch, which has a certain storage capacity, and is sold by a certain retailer. 
For example, the tuple disk\_drive (1978619, WesternDigital, A2235X, 765234, 500, CompUSA) specifies that WesternDigital 
made a disk drive with serial number 1978619, model number A2235X in batch 765235 with 500GB that is sold by CompUSA.
Which functional dependencies capture the following two requirements?\par\vspace{0.5em}
\begin{enumerate}
    \item The manufacturer and serial number uniquely identify a disk drive.
    \item A model number is registered by a manufacturer and hence can’t be used by another manufacturer.
\end{enumerate}
(Select all that apply)\par\vspace{0.5em}
\begin{checkboxes}
    \CorrectChoice manufacturer, serial\_number \texttt{->} model, batch, capacity, retailer
    \CorrectChoice model \texttt{->} manufacturer
    \choice manufacturer \texttt{->} model
    \choice manufacturer \texttt{->} serial\_number
\end{checkboxes}
\end{minipage}\vspace{1em}

\end{questions}
\end{document}