\documentclass[12pt, addpoints]{exam}
\input{preamble.tex}

\begin{document}
\noindent Name:\ \makebox[3in]{\hrulefill}\hfill Points Scored: \underline{\hspace{3em}} / \numpoints
\begin{questions}

% ------------------ TRUE/FALSE SECTION ------------------
\section*{Part I — True/False}

\begin{minipage}{\linewidth}
\question[2]
True or False: If the DDL command creating table course was changed to the below one, then a functional dependency
\textbf{\textit{title $\rightarrow$ dept\_name}} would hold on the table course.\par\vspace{0.5em}
\begin{verbatim}
create table course
(course_id varchar(8), 
title varchar(50), 
dept_name varchar(20),
credits numeric(2,0) check (credits > 0),
primary key (course_id),
unique(title),
foreign key (dept_name) references department(dept_name) on delete set null
);
\end{verbatim}
\begin{checkboxes}
    \CorrectChoice True
    \choice False
\end{checkboxes}
\end{minipage}\vspace{1em}

\begin{minipage}{\linewidth}
\question[2]
True or False: The decomposition is a Lossless Join Decomposition if the natural join of the relations 
in the decomposition produces the relation with all attributes of the original relation.\par\vspace{0.5em}
\begin{checkboxes}
    \choice True
    \CorrectChoice False
\end{checkboxes}
\end{minipage}\vspace{1em}

% ------------------ MULTIPLE SELECT SECTION ------------------
\section*{Part III — Multiple select (select all that apply)}

\begin{minipage}{\linewidth}
\question[4]
Which of the following functional dependencies hold on the University Database?\par
(Select all that apply)\par\vspace{0.5em}
\begin{checkboxes}
    \choice \textbf{\textit{ID $\rightarrow$ grade}}
    \choice \textbf{\textit{course\_id $\rightarrow$ prereq\_id}}
    \choice \textbf{\textit{building, room\_number $\rightarrow$ course\_id, sec\_id, semester, year}}
    \CorrectChoice \textbf{\textit{course\_id $\rightarrow$ title}}
\end{checkboxes}
%---\begin{solution}
%--- format for giving solution descriptions
%---\end{solution}
\end{minipage}\vspace{1em}

\begin{minipage}{\linewidth}
\question[4]
Consider the following relation disk\_drive(serial\_number, manufacturer, model, batch, capacity, retailer). 
Each tuple in the relation disk\_drive contains information about a disk drive with a unique serial\_number, made by a manufacturer, 
with a particular model, released in a certain batch, which has a certain storage capacity, and is sold by a certain retailer. 
For example, the tuple disk\_drive (1978619, WesternDigital, A2235X, 765234, 500, CompUSA) specifies that WesternDigital 
made a disk drive with serial number 1978619, model number A2235X in batch 765235 with 500GB that is sold by CompUSA.\par
Which functional dependencies capture the following two requirements?\par\vspace{0.5em}
1. All disk drives in a particular batch are the same model.\par
2. All disk drives of a particular model of a particular manufacturer have exactly the same capacity.\par\vspace{0.5em}
(Select all that apply)\par\vspace{0.5em}
\begin{checkboxes}
    \CorrectChoice batch $\rightarrow$ model
    \CorrectChoice model, manufacturer $\rightarrow$ capacity
    \choice model $\rightarrow$ capacity
    \choice manufacturer $\rightarrow$ capacity
    \choice model $\rightarrow$ batch
\end{checkboxes}
%---\begin{solution}
%--- format for giving solution descriptions
%---\end{solution}
\end{minipage}\vspace{1em}

\end{questions}
\end{document}